Stack Safety is a Security Property

### 2021-04-11 tex/main.tex
Oops

\bcp{this paragraph seems a bit in the way at the moment: the previous
  paragraph has already motivated the need for a formal characterization, so
  why not just go straight on and talk about ours?  I propose moving it to,
  say, just before ``To illustrate...''  We can also then drop the awkward
  last sentence.}
}For example, \citet{DBLP:conf/sp/RoesslerD18} describe how to protect the stack
using tag-based \emph{micro-policies}~\citep{pump_oakland2015}.
Intuitively, memory cells within each stack frame are tagged with the
identity of
the function that owns the frame, and access to those locations is then gated
according to the function that is currently executing. Roessler and Dehon
explore alternative versions
of this basic idea, with different ways of identifying
functions and deciding exactly which accesses are allowed, varying in their
efficiency and in the spatial and temporal precision of their security
guarantees.
For example, their \emph{Depth Isolation} policy demands that a function
owns any
frame into which it writes; this seems simple and intuitively correct, but can be expensive to implement.
Conversely, their \emph{Lazy Tagging and Clearing} policy improves
performance by
allowing ``illicit'' writes to inaccessible stack frames so long as the
written locations are not
subsequently read. The justification for this form of laziness is that any
genuinely dangerous writes will ultimately be
detected before they can affect program behavior. \bcp{Awkward transition here.} But we clearly need a
more formal foundation for
expressing, comparing and verifying these micro-policy security claims, as well as those of
other enforcement technologies.

>>>>

\bcp{this paragraph seems a bit in the way at the moment: the previous
  paragraph has already motivated the need for a formal characterization, so
  why not just go straight on and talk about ours?  I propose moving it to,
  say, just before ``To illustrate...''  We can also then drop the awkward
  last sentence.}
For example, \citet{DBLP:conf/sp/RoesslerD18} describe how to protect the stack
using tag-based \emph{micro-policies}~\citep{pump_oakland2015}.
Intuitively, memory cells within each stack frame are tagged with the
identity of
the function that owns the frame, and access to those locations is then gated
according to the function that is currently executing. Roessler and Dehon
explore alternative versions
of this basic idea, with different ways of identifying
functions and deciding exactly which accesses are allowed, varying in their
efficiency and in the spatial and temporal precision of their security
guarantees.
For example, their \emph{Depth Isolation} policy demands that a function
owns any
frame into which it writes; this seems simple and intuitively correct, but can be expensive to implement.
Conversely, their \emph{Lazy Tagging and Clearing} policy improves
performance by
allowing ``illicit'' writes to inaccessible stack frames so long as the
written locations are not
subsequently read. The justification for this form of laziness is that any
genuinely dangerous writes will ultimately be
detected before they can affect program behavior. \bcp{Awkward transition here.} But we clearly need a
more formal foundation for
expressing, comparing and verifying these micro-policy security claims, as well as those of
other enforcement technologies.
